\documentclass[a4paper,10pt]{article}

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[french]{babel}

%\usepackage{txfonts}
%\renewcommand{\familydefault}{\sfdefault}

\usepackage{url,xcolor,titlesec,graphicx,longtable,etaremune}
\usepackage[a4paper]{geometry}
\geometry{left=2.8cm,right=2.8cm,top=2.5cm,bottom=2.5cm}
\usepackage{fouriernc}
\usepackage[pagebackref = false]{hyperref}
\hypersetup{
  colorlinks = true,
  urlcolor = blue, 
  linkcolor = blue,
  citecolor = blue,
  pdftitle = {CV Antoine Vendeville},
  pdfauthor = {Antoine Vendeville},
  pdfsubject = {CV Antoine Vendeville}
}


\titleformat*{\section}{             
  \center
  \large \scshape%\bfseries
}

\titleformat*{\subsection}{
  \center
  \bfseries %\scshape 
}

\titleformat*{\subsubsection}{
  \center \itshape 
}

\setlength{\parindent}{0cm}

\begin{document}
%\hrule
\bigskip
\begin{center}
\LARGE\textsc{Curriculum Vit\ae}

\medskip

%\small{(Mise à jour : \today)}
\end{center}
\bigskip

%\hrule
\bigskip
\bigskip

\thispagestyle{empty} % no page numbering
 
{\large\textbf{Antoine VENDEVILLE}}
\vspace{1cm}

Born on April 23 1994 in Paris, France.

\medskip

\textbf{PhD student}\\ 
University College London\\
\href{https://www.ucl.ac.uk/cybersecurity-cdt/}{Centre for Doctoral Training in Cybersecurity}\\
Department of Computer Science

\medskip
\textbf{Supervisory team}\\
\href{https://bguedj.github.io/}{Benjamin Guedj}\\
\href{https://wp.cs.ucl.ac.uk/shizhou/}{Shi Zhou}

\medskip

\textbf{Other affiliations}\\
\href{https://www.inria.fr/en/inria-london-programme-bringing-france-and-uk-closer-together-through-research}{The Inria London program}

\medskip

\textbf{Contact}\\
  E-mail :
  \href{mailto:a.vendeville@ucl.ac.uk}{a.vendeville@ucl.ac.uk}
  
  Web : \url{https://antoinevendeville.github.io}


\renewcommand{\baselinestretch}{1.0}

\section*{Academic Positions}
\subsection*{Since 2019} 
PhD student, University College London. 
\begin{itemize}
	\item[$\bullet$] Computer Science Department
	\item[$\bullet$]\href{https://www.ucl.ac.uk/computer-science/study/postgraduate-research/centre-doctoral-training-cybersecurity}{Centre for Doctoral Training in Cybersecurity}
	\item[$\bullet$] Supervised by Supervised by \href{https://bguedj.github.io/}{Benjamin Guedj} and \href{https://wp.cs.ucl.ac.uk/shizhou/}{Shi Zhou}.
	\item[$\bullet$] Expected duration 4 years.
\end{itemize}



\subsection*{Summer 2019} 
Research assistant, Sorbonne Université\textsuperscript{\ref{note1}}.
\begin{itemize}
	\item[$\bullet$] Computer Science Department (\href{https://www.lip6.fr/}{LiP6}), team \href{https://www-npa.lip6.fr/}{NPA}.
	\item[$\bullet$] Supervised by \href{https://anastasiosgiovanidis.net/}{Anastasios Giovanidis}, \href{https://www.lip6.fr/actualite/personnes-fiche.php?ident=P144}{Bruno Baynat}, \href{https://www-complexnetworks.lip6.fr/~magnien/}{Clémence Magnien}.
	\item[$\bullet$] Duration 5 months.
\end{itemize}

\subsection*{Summer 2018} 
Research assistant, Sorbonne Université\textsuperscript{\ref{note1}}.
\begin{itemize}
	\item[$\bullet$] Computer Science Department (\href{https://www.lip6.fr/}{LiP6}), team \href{https://www-npa.lip6.fr/}{NPA}.
	\item[$\bullet$] Supervised by \href{https://anastasiosgiovanidis.net/}{Anastasios Giovanidis}, \href{https://www.lip6.fr/actualite/personnes-fiche.php?ident=P144}{Bruno Baynat}, \href{https://www-complexnetworks.lip6.fr/~magnien/}{Clémence Magnien}.
	\item[$\bullet$] Duration 5 months.
\end{itemize}

\section*{Publications}

\subsection*{2022}
$\bullet$ A. Vendeville, B. Guedj and S. Zhou. Depolarising Social Networks: Optimisation of Exposure to Adverse Opinions in the Presence of a Backfire Effect. Submitted. Preprint on \href{https://arxiv.org/abs/2203.02002}{arXiv}, \href{https://hal.inria.fr/hal-03600429}{HAL}.

$\bullet$ A. Vendeville, B. Guedj and S. Zhou. Towards control of opinion diversity by introducing zealots into a polarised social group. \href{https://link.springer.com/chapter/10.1007\%2F978-3-030-93413-2_29}{Proceedings of Complex Networks and Their Applications X}. Preprint on \href{https://arxiv.org/abs/2006.07265}{arXiv}, \href{https://hal.inria.fr/hal-02872161}{HAL}.

\subsection*{2021}
$\bullet$ A. Giovanidis, B. Baynat, C. Magnien and A. Vendeville. Ranking Online Social Users by Their Influence. \href{https://doi.org/10.1109/TNET.2021.3085201}{IEEE/ACM Transactions on Networking, 2021}. Preprint on \href{https://arxiv.org/abs/2107.01914}{arXiv}, \href{https://hal.archives-ouvertes.fr/hal-02970215}{HAL}.

$\bullet$ A. Vendeville, B. Guedj and S. Zhou. Forecasting elections results via the voter model with stubborn nodes. \href{https://doi.org/10.1007/s41109-020-00342-7}{Applied Network Science 6, 1, 2021}. Preprint on \href{https://arxiv.org/abs/2009.10627}{arXiv}, \href{https://hal.archives-ouvertes.fr/hal-02946434}{HAL}.

\subsection*{2019}
$\bullet$ A. Giovanidis, B. Baynat and A. Vendeville. Performance Analysis of Online Social Platforms. \href{https://ieeexplore.ieee.org/abstract/document/8737539}{IEEE INFOCOM 2019, pp. 2413-2421}. Preprint on \href{https://arxiv.org/abs/1902.07187}{arXiv}, \href{https://hal.archives-ouvertes.fr/hal-01941296}{HAL}.


\section*{Talks and Presentations}
\subsection*{2022}
$\bullet$ \href{https://antoinevendeville.github.io/files/talk_IDS.pdf}{Voter model with zealots for opinion control and forecast of election results}, presented on January 7, 2022 at University College London, for the Information and Decision Systems research group \href{https://www.ucl.ac.uk/computer-science/research/research-groups/information-and-decision-systems-ids}{IDS}.

\subsection*{2021}
$\bullet$ \href{https://antoinevendeville.github.io/files/poster_complexnet21.pdf}{Towards control of opinion diversity by introducing zealots into a polarised social group}, poster presented on December 1, 2021 at \href{https://complexnetworks.org/}{Complex Networks 2021}.

$\bullet$ \href{https://antoinevendeville.github.io/files/talk_networks21.pdf}{Voter Model with Stubborn Agents: from Theoretical Solutions to Prediction of Political Elections}, presented on July 5, 2021 at \href{https://networks2021.net/}{Networks 2021}.

\section*{Teaching}
\textbf{2021} \href{https://bguedj.github.io/}{Benjamin Guedj} and I supervised \href{https://valentinkil.github.io/}{Valentin Kilian} for a 2 months research internship on opinion dynamics at \href{https://www.inria.fr/en}{Inria}.

\textbf{2019-2022} teaching assistant at University College London for \href{https://www.ucl.ac.uk/module-catalogue/modules/complex-networks-and-web/COMP0123}{Complex Networks and Web (COMP0123)}.

\textbf{2020-2021} teaching assistant at University College London for \href{https://www.ucl.ac.uk/module-catalogue/modules/introductory-programming/COMP0066}{Introductory Programming (COMP0066)}.

\textbf{2013-2016} private maths tutor for high school students in Paris.

\section*{Education}
\textbf{2018-2019} Master 2 Data Science, Université Claude Bernard, Lyon.

\textbf{2017-2018} Master 2 Mathematical Modelling, Sorbonne Université\textsuperscript{\ref{note1}}.

\textbf{2015-2017} Master 1 Mathematics and Applications, Sorbonne Université\textsuperscript{\ref{note1}}.

\textbf{2012-2015} Bachelor in Mathematics and Applications, Sorbonne Université\footnote{\label{note1}Former Université Pierre et Marie Curie, Paris, France.}.


\section*{Peer Reviews}
I have reviewed papers for the following journals.
\begin{itemize}
	\item[$\bullet$] \href{https://www.nature.com/srep/}{Nature Scientific Reports}
	\item[$\bullet$] \href{https://journals.plos.org/plosone/}{PLOS ONE}
	\item[$\bullet$] \href{https://royalsocietypublishing.org/journal/rspa}{Proceedings of the Royal Society A}
	\item[$\bullet$] \href{https://www.journals.elsevier.com/computer-communications}{Computer Communications}
\end{itemize}

 \thispagestyle{empty} % no page numbering

\end{document}
